Adaptive Disk Storage for Interaction Graphs

### 2014-09-09 docs/edbt2015/text/paper.tex
removed text
outline

@@

>>>>

\section{System Overview}

\begin{alltt}\scriptsize
- Intro
    - What is an interaction graphs
    - Relationship graphs vs interaction graphs 
        - interactions get big
- System overview
    - How interaction graph are currently stored
    - Introduce the rail layout
- Layout or partitioning problem 
    - Cost model
- Optimal Solutions
- Heuristic solutions
\end{alltt}

@@

\section{Conclusion}
